---
title: "Rentals Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## upload data


```{r upload}
library(dplyr)
library(lubridate)
library(ggplot2)
library(stringr)
library(sp)
library(leaflet)
rental <- read.csv("rental.csv")
rentals <- tbl_df(rental)
```

## Number of rental properties for each agency:

```{r properties}
rentals%>%
  group_by(Agency)%>%
  summarise(num = n())%>%
  arrange(desc(num))

```

Note that LJ Hooker - Belconnen and Ray White - Canberra post the most number of properties on the list in last month.

## Bar chart:
This chart shows that the total number of properties in each suburb.

```{r bar}
#rental%>%
#  group_by(Suburb)%>%
#  mutate(count = n())%>%
#  arrange(desc(count))%>%
#  select(Suburb, count)
#  ggplot(data = rentals, mapping = aes(x = reorder(Suburb, count), y = count)) + theme_bw() + geom_bar(stat = 'identity') + theme(axis.text.x = element_text(face = "bold", angle = 45)) + theme(panel.border = element_blank()) + theme(panel.grid = element_blank()) + 
#  labs(y = "number of properties", title = "Total counts in each suburb")
```

## Map chart:
This chart shows the location of each property and the rent for each property.

```{r map}
rentals$long <- as.numeric(rentals$Longitude)
rentals$lat <- as.numeric(rentals$Latitude)
rentals.sp <- SpatialPointsDataFrame(rentals[,c(7,8)], rentals[,-c(7,8)])

m <- leaflet()%>%
  addTiles()%>%
  addMarkers(data = rentals, lng = ~Longitude, lat = ~Latitude, popup = (~First.Listed.Price))
m
 

```

## Total rental properties were provided by each agency in each suburb:

```{r total properties}
rentals%>%
  group_by(Suburb,Agency)%>%
  tally()
```

## Average rental price in each suburb per week:

```{r rent}
rentals%>%
  group_by(Suburb)%>%
  summarise(avg_price = mean(First.Listed.Price.Guide, na.rm = TRUE ))%>%
  arrange(desc(avg_price))
```

The rental prices are expensive at Latham and Melba, whatsmore, Charnwood has the cheapest rental price.

## Price different % between listed and price guide

```{r diff}
rentals%>%
  select(Agency,Suburb, Price.Guide, First.Listed.Price.Guide)%>%
  mutate(Percentage = (((First.Listed.Price.Guide - Price.Guide)/Price.Guide))*100)%>%
  arrange(Percentage)
```

## Average rental price in each type of room per week:

```{r price}
bed_no = c(3,4)
bath_no = c(1,2)

for (i in bed_no) {
  for (j in bath_no) {
    rentals%>%
      filter(Bedrooms == i, Bathrooms == j)%>%
      summarise(ave_price = mean(First.Listed.Price.Guide, na.rm = TRUE))%>%
      print()
  }
}
```

3 beds and 1 bath average rental price: $456/week;

3 beds and 2 baths average rental price: $545/week;

4 beds and 1 bath average rental price: $625/week;

4 beds and 2 baths average rental price: $618/week

## How many properties has been listed for each week by each agency:

```{r by week}
rentals%>%
  mutate(week = isoweek(as.Date(First.Listed)))%>%
  group_by(week, Agency)%>%
  summarise(num = n())

rentals%>%
  mutate(week = isoweek(as.Date(First.Listed)))%>%
  group_by(week)%>%
  summarise(num = n())
```


