---
title: "Sales Analysis"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data information:
There are 20 different Agencies and data shows us the properties which were on the sales listing in last month and in ACT, Australia.

This report shows the following results in the analysis:

1.Total number of properties by each Agency.

2.The location of each property.

3.Average price for each type of property.

4.Average price for property in each suburb.

5.Total number of properties had been listed by each Agency in each suburb.

6.Number of properties had been listed in each week.

## upload data

```{r echo=FALSE}
sales <- read.csv("sales.csv")
library(dplyr)
library(lubridate)
library(ggplot2)
library(stringr)
library(sp)
library(leaflet)
sales1 <- tbl_df(sales)
```

## For each agency, how many properties they post on the list:

```{r agency}
sales1%>%
  group_by(Agency)%>%
  summarise(total_num = n())%>%
  select(Agency, total_num)%>%
  arrange(desc(total_num))

```

Note that LJ Hooker Kippax - Holt and Ray White - Canberra post the most properties on the list in last month.

## Bar chart:
This chart shows that the total number of properties in each suburb.

```{r bar}
ggplot(sales1, aes(x = Suburb)) + theme_bw() + geom_bar() + theme(axis.text.x = element_text(face = "bold", angle = 45)) + theme(panel.border = element_blank()) + theme(panel.grid = element_blank()) +
  labs(y = "number of properties", title = "Total counts in each suburb")
```

## Map chart:
This chart shows the location of each property.

```{r map}
devtools::install_github('rstudio/leaflet')
sales1$long <- as.numeric(sales1$Longitude)
sales1$lat <- as.numeric(sales1$Latitude)
sales1.sp <- SpatialPointsDataFrame(sales1[,c(7,8)], sales1[,-c(7,8)])

m <- leaflet()%>%
  addTiles()%>%
  addMarkers(data = sales1, lng = ~Longitude, lat = ~Latitude, popup = ~Suburb)
m


 #ggplot() + geom_point(data = sales1, aes(x = Longitude, y = Latitude), color = "red")

```

## For each type of the property, what is the average sales price guide:

```{r price guide}
sales1%>%
  group_by(Property.Type)%>%
  summarise(avg_guide = mean(Price.Guide, na.rm = TRUE), n = n())
```

## The average price for each suburb:

```{r suburb}
sales1%>%
  group_by(Suburb)%>%
  summarise(ave_first_listed = mean(First.Listed.Price.Guide, na.rm = TRUE), ave_price_guide = mean(Price.Guide, na.rm = TRUE))%>%
  arrange(desc(ave_first_listed),desc(ave_price_guide))

```

The properties in McKellar are much more expensive than other suburbs.

## How many properties that each agency post in each suburb:

```{r property in each suburb}
sales1%>%
  group_by(Suburb,Agency)%>%
  tally()%>%
  print.data.frame()

```

## How many properties has been listed for each week by each agency:

```{r by week}
sales1%>%
  mutate(week = isoweek(as.Date(First.Listed)))%>%
  group_by(week,Agency)%>%
  summarise(num = n()) 

sales1%>%
  mutate(week = isoweek(as.Date(First.Listed)))%>%
  group_by(week)%>%
  summarise(num = n())

```












